---
title: "Scraping homework"
author: "Thorkil"
date: "18/3/2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Goals of this script
This markdown file describes cleans the text-data that I scraped from the parliament websites. It also sorts out the relevant statements to look at. 

## 1.1 Bare neccessities
I start by loading all the packages I will need
```{r, message=F}
#Remove all objects
#rm(list = ls()) 

library(rvest) # To scrape web data
library(dplyr) #To manipulare data
library(stringr) #To work with strings in a concise way
library(httr) #To access anf get data from the twitter-api
library(rebus) #An intuitive guide to regular expressions
library(lubridate) #To work with dates and time date
library(ggplot2) #To plot!
```

# 2.Adding additional variables
I start by loading the data
```{r}
#Load the respective data sets
getwd()

#Make a list to contain the data
resumes_load <- vector("list", length = 11)

#Load the data into the list
setwd("/Users/thorkilklint/Documents/Berkeley/PS239T_Computational/ps239T-final-project/Data")
for (i in 1:length(resumes_load)){
  resumes_load[[i]]<-readRDS(paste0("resume_debate_",i,".Rda"))
}
```

## 2.1 Is the speaker chairman of the session?

I make a new variable, indicating wether the speaker is the chair of the session
```{r}
for (i in 1:length(resumes_load)){
  resumes_load[[i]]$chairman <- str_detect(resumes_load[[i]]$V1, "Formand|formand")
  #Move speaker one down, as the split seperated them
  resumes_load[[i]]$chairman[2:nrow(resumes_load[[i]])]<-resumes_load[[i]]$chairman[1:nrow(resumes_load[[i]])-1]
}
```

## 2.2 Education and party of the speaker
I load the member data
```{r}
#Load the member data
setwd("/Users/thorkilklint/Documents/Berkeley/PS239T_Computational/ps239T-final-project/Data")
all_members_df<-readRDS("all_members_data.Rda")

#I make a shorter version of member data withoutunimportant variables
member_df_merge <- dplyr::select(all_members_df, -biografi, -typeid, -education) 
```

And then I can merge the member data with the resume data to get speaker party and education
```{r}
#I merge the datasets with the member information
for (i in 1:length(resumes_load)){
  resumes_load[[i]]<-dplyr::left_join(resumes_load[[i]], member_df_merge, by = "name")
}
```

## 2.3 Make variables into correct format
My data work has made some of the variables into incorrect formats
```{r}
str(resumes_load[[1]])
```
V2, the text variable, is currently a factor, which is incorrect. I make it into a character, and rename it to "text"
```{r}
for (i in 1:length(resumes_load)){
  resumes_load[[i]]$text<-as.character(resumes_load[[i]]$V2)
}
#Then, I can check out the structure
str(resumes_load[[1]]) 
```

And then, I can remove V1 and V2 from the dataset
```{r}
for (i in 1:length(resumes_load)){
  resumes_load[[i]]<-dplyr::select(resumes_load[[i]], -V1, -V2)
}
#Then, I can check out the structure
str(resumes_load[[1]]) 
```

# 3. Finding statements relevant to migration debate
Although a lot of the debates that I have drawn are about immigration, they are not all about immigration. I therefore have to solve two things before I save my data

1. I have to find the statements that are actually made during an immigration debate
2. I have to sort out the chairmans comments, as these are more of meta statements, and therefore not relevant in regards to my project.

The reason I am doing this in this order, is to allow me to use the chairman commens as splits

## 3.1. Finding the relevant statements
I have to get an overview of the sequence of the statements, as not all of the debates are about immigration  

I draw the agenda point for each statement in the debate
```{r}
#For agenda item logical
next_agenda_item_pattern <- "første punkt på dagsordenen er:|næste punkt på dagsordenen er:"

#Set a pattern for bill propositions
## In resumes with new line
proposition_pattern_new_line <- "[:space:]" %R% "[:digit:]{1,2}" %R% "\\)" %R% "[:space:][:digit:]" %R% ".*"
## In resumes with no line
proposition_pattern_no_line <- "[:digit:]{1,2}" %R% "\\)" %R% "[:space:][:digit:]" %R% ".*" %R% "[:digit:]" %R% "\\:"
## Together
proposition_pattern<-rebus::or(proposition_pattern_new_line,proposition_pattern_no_line)

#Set a pattern for content of bill propositions
## In resumes with new line
content_pattern_new_line <- "[:space:]" %R% "Forslag til .*"
## In resumes with no line
content_pattern_no_line <- "Forslag til .*" %R% "\\).Af"
## Together
content_pattern<-rebus::or(content_pattern_new_line,content_pattern_no_line)

## Get the bill proposition agenda points from a loop, and make a variable called agenda item
for (i in 1:length(resumes_load)){
  propositions<-str_extract(resumes_load[[i]]$text,pattern=proposition_pattern)
  content<-str_extract(resumes_load[[i]]$text,pattern=content_pattern)
  prop_content<-paste0(propositions,content)
  resumes_load[[i]]$agenda_item<-prop_content
}

#For agenda question
##For the first agenda question
first_agenda_question_pattern<-"første spørgsmål" %R% ".*" %R% "\\."

##For the second agenda question
next_agenda_question_pattern<-"næste spørgsmål" %R% ".*" %R% "\\."

## Together
question_pattern<-rebus::or(first_agenda_question_pattern,next_agenda_question_pattern)

#Make a variable for agenda question
for (i in 1:length(resumes_load)){
  resumes_load[[i]]$agenda_question<-str_extract(resumes_load[[i]]$text,pattern=question_pattern)
}

#Put the two agenda variables together
for (i in 1:length(resumes_load)){
  ## Make a new variable two merge with, out of the agenda questions
  resumes_load[[i]]$agenda<-resumes_load[[i]]$agenda_question
  ##Ad the agenda questions, where there is an agenda question
  resumes_load[[i]]$agenda[resumes_load[[i]]$agenda_item!="NANA"]<-resumes_load[[i]]$agenda_item[resumes_load[[i]]$agenda_item!="NANA"]
  resumes_load[[i]]<-select(resumes_load[[i]], -agenda_item, -agenda_question)
}
```

Now, I have an agenda variable, showing when the agenda item switches, and what it switches to.I can use this, to get an overview of the debate
```{r}
#I make an indicator variable
for (i in 1:length(resumes_load)){
  resumes_load[[i]]$statement_number<-1:nrow(resumes_load[[i]])
}
```

### 3.1.1 Picking the statements from Debate 1
```{r, eval=F}
View(resumes_load[[1]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need row 220 to nrow(resumes_load[[1]])
```{r}
resumes_load[[1]]<-filter(resumes_load[[1]], statement_number>219)
```

### 3.1.2 Picking the statements from Debate 2
```{r, eval=F}
View(resumes_load[[2]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need row 106 to nrow(resumes_load[[2]])
```{r}
resumes_load[[2]]<-filter(resumes_load[[2]], statement_number>105)
```

### 3.1.3 Picking the statements from Debate 3
```{r, eval=F}
View(resumes_load[[3]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need row 189 to nrow(resumes_load[[3]])
```{r}
resumes_load[[3]]<-filter(resumes_load[[3]], statement_number>188)
```

### 3.1.4 Picking the statements from Debate 4
```{r, eval=F}
View(resumes_load[[4]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need row 206 to 277
```{r}
resumes_load[[4]]<-filter(resumes_load[[4]], statement_number>205 & statement_number<278)
```

### 3.1.5 Picking the statements from Debate 5
```{r, eval=F}
View(resumes_load[[5]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I dont need anything

### 3.1.6 Picking the statements from Debate 6
```{r, eval=F}
View(resumes_load[[6]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I dont need anything

### 3.1.7 Picking the statements from Debate 7
```{r, eval=F}
View(resumes_load[[7]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need 36-198
```{r}
resumes_load[[7]]<-filter(resumes_load[[7]], statement_number>35 & statement_number<199)
```

### 3.1.8 Picking the statements from Debate 8
```{r, eval=F}
View(resumes_load[[8]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need 100-160
```{r}
resumes_load[[8]]<-filter(resumes_load[[8]], statement_number>99 & statement_number<161)
```

### 3.1.9 Picking the statements from Debate 9
```{r, eval=F}
View(resumes_load[[9]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need 83-143 and 314-nrow(resumes_load[[9]])
```{r}
resumes_load[[9]]<-filter(resumes_load[[9]], statement_number>82 & statement_number<144 | statement_number>313)
```

### 3.1.10 Picking the statements from Debate 10
```{r, eval=F}
View(resumes_load[[10]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need 71-122 and 191-nrow(resumes_load[[10]])
```{r}
resumes_load[[10]]<-filter(resumes_load[[10]], statement_number>70 & statement_number<123 | statement_number>190)
```

### 3.1.11 Picking the statements from Debate 11
```{r, eval=F}
View(resumes_load[[11]] %>%
  select(statement_number, agenda) %>%
  filter(!is.na(agenda)))
```
Here, I need 106-nrow(resumes_load[[11]])
```{r}
resumes_load[[11]]<-filter(resumes_load[[11]], statement_number>105)
```

## 3.2 Making one data frame
Now, I can collect all the statements into one data frame
```{r}
immigration_debate_text_data <- bind_rows(resumes_load[[1]],
                                          resumes_load[[2]],
                                          resumes_load[[3]],
                                          resumes_load[[4]],
                                          resumes_load[[7]],
                                          resumes_load[[8]],
                                          resumes_load[[9]],
                                          resumes_load[[10]],
                                          resumes_load[[11]])
```
The time variable is currently a character, why I change it with the lubridate package
```{r}
immigration_debate_text_data$time<-hm(immigration_debate_text_data$time)
#Then, I can check out the structure
str(immigration_debate_text_data) 
```

# 4. Removing the chairman comments
Now, all that I have to do, is to remove the chairman comments. Further, I remove the comment "Værsgo", which just yields the floor.  
```{r}
immigration_debate_text_data<-filter(immigration_debate_text_data, chairman==F) #Remove chairman comments
immigration_debate_text_data<-filter(immigration_debate_text_data, !str_detect(immigration_debate_text_data$text, pattern="Værsgo.")) #Remove "Værsgo."
```

# 5. Save the data
And now, I can save these data frames as one big R data frame!
```{r}
getwd()
setwd("/Users/thorkilklint/Documents/Berkeley/PS239T_Computational/Final Project/Scripts/get_data")
saveRDS(immigration_debate_text_data,file="immigration_debate_text_data.Rda")
write.csv(immigration_debate_text_data,file="immigration_debate_text_data.csv")
```
