---
title: "Topic Modelling"
author: "Thorkil"
date: "23/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Goals of this script
This script aims at conducting a introductory topic model for the textdata from the Danish Parliament debates

## 2. Necessities
```{r, message=F}
rm(list=ls())
library(stringr) #For working with string data
library(tm) # Framework for text mining
library(ggplot2) # for plotting word frequencies
library(dplyr)
library(RTextTools) # a machine learning package for text classification written in R
library(SnowballC) # for stemming
library(data.table)
library(wordcloud2) # for wordclouds
library(RColorBrewer) # for color palettes
library(matrixStats) # for statistics
library(ggplot2) #For plotting
```

# STEP 1: PRE PROCESS AND CLEAN THE TEXT
I start by opening my statement dataset
```{r}
#Open the data
getwd()
setwd("/Users/thorkilklint/Documents/Berkeley/PS239T_Computational/ps239T-final-project/Data")
immigration_debate_text_data<-readRDS("immigration_debate_text_data.Rda")
```
When using the tm-package to structure text data in the corpus format, the importet data-set has to have the following collumns in order: 
1. doc_id - a unique string for each document
2. text - the text to be examined
... - any other columns will be automatically cataloagued as meta-data.

I set up the doc_id variable. I give this variable intuitive names based on the party of the speaker, as this allows me to split the dataset into different parties / political blocs later on
```{r}
#A doc ID variable with party name and number of statement, so that I can sort
immigration_debate_text_data$doc_id <- paste0(immigration_debate_text_data$party, "_",
                                             1:nrow(immigration_debate_text_data))
```
Further, the text data contains to symbols, not recognized by R as punctuation, namely » and «. I remove these.
```{r}
#The remove unctuation function further on does not remove » or «
sum(str_detect(immigration_debate_text_data$text, "«"))
sum(str_detect(immigration_debate_text_data$text, "»"))

immigration_debate_text_data$text<-str_replace_all(immigration_debate_text_data$text, pattern="«|»", "")

sum(str_detect(immigration_debate_text_data$text, "«"))
sum(str_detect(immigration_debate_text_data$text, "»"))
```

Now, I just have to reorder the variables
```{r}
#Reorder the variables
immigration_debate_text_data<-select(immigration_debate_text_data, doc_id, text,name, time, party, academic)

#Check out the structure
str(immigration_debate_text_data)
```